---
title: "Plotly example"
author: "Bruno Ascenso"
date: "November 16, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
library(gapminder)
data(gapminder)
```

## Overview

This presentation week 2 assignment of the course Developing Data Products on Coursera.

The instructions were:  
"*Create a web page presentation using R Markdown that features a plot created with Plotly*".  

So I decided to look in the plotly website for some advanced examples and learn one of them to use in this assignment.

## Code used

This is the code used to create the plot:
```{r code, echo=TRUE, results = FALSE, eval=FALSE}
p <- ggplot(gapminder, aes(gdpPercap, lifeExp, color = continent)) +
    geom_point(aes(size = pop, frame = year, ids = country)) +
    labs(x = "GDP per capita", y = "Life Expectancy") +
    scale_x_log10()

ggplotly(p) %>% 
    animation_opts(1000, easing = "elastic", redraw = FALSE) %>% 
    animation_button(x = 1, xanchor = "right", 
                     y = 0, yanchor = "bottom") %>%
    animation_slider(currentvalue = 
                list(prefix = "YEAR ", font = list(color="red")))

```

## Plot
And this is the plot. Press the **Play** button or move the slider.

```{r plot, echo = FALSE, results = TRUE}
suppressWarnings(p <- ggplot(gapminder, aes(gdpPercap, lifeExp, color = continent)) +
    geom_point(aes(size = pop, frame = year, ids = country)) +
    labs(x = "GDP per capita", y = "Life Expectancy") +
    scale_x_log10())

ggplotly(p) %>% 
    animation_opts(1000, easing = "elastic", redraw = FALSE) %>% 
    animation_button(x = 1, xanchor = "right", y = 0, yanchor = "bottom") %>%
    animation_slider(currentvalue = list(prefix = "YEAR ", font = list(color="red")))

```

## Thanks for reviewing
